### 2014-08-03 paper/paper.tex
Added a section about cross validation. Included the second graph and fixed the cross validation

    %TODO talk about cross validation

@@

After the SemEval-2013 workshop the organizers released a paper discussing the
proceedings and the results of the task \cite{Nakov2013}. The paper establishes
baseline in terms of $F$. $F$ can be calculated as:
\begin{equation}
    F = \frac{2 \frac{P_{pos}R_{pos}}{P_{pos} + R_{pos}} +
    2 \frac{P_{neg}R_{neg}}{P_{neg} + R_{neg}}}{2}
\end{equation}

@@

@@

The baseline for this project is established by running the Maximum Entropy
classifier without any Stop word removal, Uncommon word removal, Or feature
Normalization. The F-score that is achieved is 50.72. See Experiment \textit{g}
in Table \ref{table:results} to see the results in context.

@@

Since the \textit{test set} is random subset of the corpus, the results of the
classifier can vary slightly between runs. In order to effectively evaluate the
performance of the classifier under certain conditions each experiment is
conducted 3 times and averaged.

\begin{table}[H]
    \begin{center}
    \begin{tabular}{|r||c|c|}
        \hline
           Description    & mean F & std F  \\
        \hline
           All            & 0.0   & 0.0    \\
           Just Stopwords & 0.0    & 0.0    \\
           Just Uncommon  & 0.0    & 0.0    \\
           Just Normalize & 0.0    & 0.0    \\
           Baseline       & 0.0    & 0.0    \\
        \hline
    \end{tabular}
    \end{center}
    \caption{Holla!}
    \label{table:results}
\end{table}

\begin{figure}[H]
    \includegraphics{figures/maxent_boxplot.png}
    \caption{Caption...}
    \label{figure:maxent}
\end{figure}

The results in Table \ref{table:results} indicates that there is not lot of
difference variation between experiments. The best average F-score is
experiment \textit{g}, however $\sigma_{g} = 2.69$. In contrast, the second
best F-score is experiment \textit{a} exhibits more consistent classification
with $\sigma_{a} = 1.04$.

\begin{table}[H]
    \begin{center}
    \begin{tabular}{|c||r|r|r|r|r|}
        \hline
                               & Positive & Neutral & Negative & Overall & Total \\
        \hline
        \textit{a}, \textit{i} & 14.85    & 14.06   & 15.10    & 14.49   & 5964 \\
        \textit{b}, \textit{j} & 14.91    & 14.30   & 15.30    & 14.67   & 7493 \\
        \textit{c}, \textit{k} & 15.95    & 15.40   & 16.33    & 15.73   & 0 \\
        \textit{d}, \textit{l} & 17.13    & 16.86   & 17.41    & 17.04   & 0 \\
        \textit{e}, \textit{m} & 18.54    & 17.81   & 18.82    & 18.22   & 5993 \\
        \textit{f}, \textit{n} & 18.43    & 17.87   & 18.85    & 18.21   & 7522 \\
        \textit{g}, \textit{o} & 19.64    & 19.15   & 20.05    & 19.46   & 0 \\
        \textit{h}, \textit{p} & 20.65    & 20.45   & 20.96    & 20.58   & 0 \\
        \hline
    \end{tabular}
    \end{center}
    \caption{`Positive', `Neutral', `Negative', and `Overall' refer to the
    average number of features per Tweet in each experiment. `Total' refers to
    the total number of different features in the dataset}
    \label{table:numfeatures}
\end{table}

>>>>

@@

After the SemEval-2013 workshop the organizers released a paper discussing the
proceedings and the results of the task \cite{Nakov2013}. The paper establishes
baseline in terms of $F$. $F$ can be calculated as:

\begin{equation}
    F = \frac{2 \frac{P_{pos}R_{pos}}{P_{pos} + R_{pos}} +
    2 \frac{P_{neg}R_{neg}}{P_{neg} + R_{neg}}}{2}
\end{equation}

@@

\subsection{Smooth Performance Measurement}

    Testing the performance of the system with a single run can produce skewed
    results since whether `easy' Tweets end up in \textit{training set} or the
    \textit{test set} will affect performance. To combat this the following
    \textbf{exhaustive cross-validation} method is used:

        \item \textbf{Partitioning} - The corpus of documents are shuffled and
            separated into 5 or 10 sections.

        \item \textbf{Folding} - The training and testing process are run
            multiple times with sections used for various roles. The roles are
            permuted so that the classifier is trained and tested with the
            sections in all possible configurations. In each fold 60\% of the
            partitions are designated as part of the \textit{training set},
            20\% as the \textit{validation set}, and 20\% as the \textit{test set}.
            Since the Naive Bayes classifier does not use a validation set
            40\% of the partitions are designated as part of the \textit{test set}

            %TODO is this clear?

            \item \textbf{Training} - The classifier is trained with the
                partitions designated as part of the \textit{training set} for
                the fold. The Maximum Entropy classifier also uses the
                \textit{validation set} to determine when to stop the training
                process.

            \item \textbf{Testing} - The performance of the classifier is
                evaluated using the \textit{test set} and the results are recorded.

        \item \textbf{Aggregating} - The results from all folds are averaged.

@@

The baseline for this project is established by running the Maximum Entropy
classifier without any stopword removal, uncommon word removal, Or feature
normalization. The F-score that is achieved is 50.72. See Experiment \textit{g}
in Table \ref{table:maxent-results} to see the results in context.

\subsection{Number of features}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{|c||r|r|r|r|r|}
        \hline
        Description        & Positive & Neutral & Negative & Overall & Total \\
        \hline
        All                & 14.85    & 14.06   & 15.10    & 14.49   & 5964 \\
        Just Stopwords     & 15.95    & 15.40   & 16.33    & 15.73   & 0 \\
        Just Uncommon      & 18.54    & 17.81   & 18.82    & 18.22   & 5993 \\
        Just Normalization & 19.64    & 19.15   & 20.05    & 19.46   & 0 \\
        Baseline           & 20.65    & 20.45   & 20.96    & 20.58   & 0 \\
        \hline
    \end{tabular}
    \end{center}
    \caption{`Positive', `Neutral', `Negative', and `Overall' refer to the
    average number of features per Tweet in each experiment. `Total' refers to
    the total number of different features in the dataset}
    \label{table:numfeatures}
\end{table}

@@

\subsubsection{Maximum Entropy Classifier}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{|r||c|c|}
        \hline
           Description    & mean F & std F \\
        \hline
           All            & 0.0    & 0.0   \\
           Just Stopwords & 0.0    & 0.0   \\
           Just Uncommon  & 0.0    & 0.0   \\
           Just Normalize & 0.0    & 0.0   \\
           Baseline       & 0.0    & 0.0   \\
        \hline
    \end{tabular}
    \end{center}
    \caption{Performance of the Maximum Entropy classifier using exhaustive
    cross-validation with 5 partitions}
    \label{table:maxent-results}
\end{table}

\begin{figure}[H]
    \begin{center}
    \includegraphics[scale=0.75]{figures/maxent_boxplot.png}
    \caption{Caption...}
    \label{figure:maxent}
    \end{center}
\end{figure}

\subsubsection{Naive Bayes Classifier}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{|r||c|c|}
        \hline
           Description    & mean F & std F \\
        \hline
           All            & 0.0    & 0.0   \\
           Just Stopwords & 0.0    & 0.0   \\
           Just Uncommon  & 0.0    & 0.0   \\
           Just Normalize & 0.0    & 0.0   \\
           Baseline       & 0.0    & 0.0   \\
        \hline
    \end{tabular}
    \end{center}
    \caption{Performance of the Naive Bayes classifier using exhaustive
    cross-validation with 5 partitions}
    \label{table:bayes-results}
\end{table}

\begin{figure}[H]
    \begin{center}
    \includegraphics[scale=0.75]{figures/bayes_boxplot.png}
    \caption{Caption...}
    \label{figure:bayes}
    \end{center}
\end{figure}
